Agile Monitoring of Evolving Web Services: For the Little Man

### 2018-04-07 introductory.tex
...

  The \tool has been deployed with the case study API for 
  ten months (between June 2017 and the time of writing this
  article, April 2018), time in which more than 112.000 hits 
  of the API have been recorded. The highest load observed 
  until now on the API consisted of 12K requests in a single day.

>>>>

  The \tool has been deployed with the case study API for 
  ten months (between June 2017 and the time of writing this
  article, April 2018), time in which more than 112.000 requests
  to the API have been recorded \footnote{This is a lower bounds
  on usage, as only a subset of the API endpoints have been 
  actually instrumented} . The highest load observed 
  until now on the API consisted of 12K requests in a single day. 
  With the help of the applications in the ecoystem the users have 
  performed about 30K vocabulary exercises and have translated 
  about 28K words and experssions while reading foreign language 
  texts.
